Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-19 demystify.tex
updates

The focus of the admissions committee is to \textbf{evaluate your background and interest in research} to see if you can handle a PhD in CS, which is a \emph{research} degree!. We also aim to determine if you would \textbf{fit into the program}. To evaluate your profile, we consider
the following key indicators.

@@

\section{Why did I get rejected?}\label{sec:why-rejected}
Many possible reasons!  Other than not having a strong profile (e.g., research potential, GPA, LoRs, SOP, poor interviews), here are some other reasons.

@@

\paragraph{Not a good fit}  You could have an excellent profile, but if you are interested in a research area that the program does not have, you might not be admitted.
Similarly, if there is no faculty who is willing to advise you (e.g., they are on sabbatical or personal leave, do not have sufficient funding, or already have too many students already), you will not be admitted.  This is actually good for you, as you don't want to be in a program where no one can advise you.

>>>>

The focus of the admissions committee is to evaluate your background and interest in research to see if you \textbf{fit} into our program and can handle a PhD in CS, which is a \emph{research} degree!  To evaluate your profile, we consider the following key indicators.

@@

\section{Why did I get rejected?}\label{sec:why-rejected}

Many students lament that they have a good profile, but still got no interviews or rejected, and that the process seems random.  However, while it is true that the process is not perfect, it is not random.  The short answer is that you do not "fit" the program or the prof.  Why?

Many possible reasons!  Other than not having a strong profile (e.g., research potential, GPA, LoRs, SOP, poor interviews), here are some other reasons.

@@

\paragraph{Not a good fit}  You could have an excellent profile, but if you are interested in a research area that the program does not have, you might not be admitted.
Similarly, if no faculty who is willing to advise you (e.g., they are on sabbatical or personal leave, do not have sufficient funding, or already have too many students already), you will not be admitted.  This is actually good for you, as you don't want to be in a program where no one can advise you.
